---
title: "Meta-analysis tutorial"
author: "AJ Fowler"
date: "16/09/2020"
output: ioslides_presentation
---
<!--    background color = #0d3273 -->

<!--  Add banner for future -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<!-- custom css styling -->
``` {css, echo=FALSE}
p {
  color:dimgrey}

h1,h2,h3,h4,h5,h6,h7{
  colour: dimgrey;
  font-style: 1.1em;
}
```

## Meta-Analysis

Meta-analysis is the statistical combination of multiple studies. 

It forms the analytic component of a quantitative systematic review.

Meta-analyses of high quality randomised trials are considered to be the highest level of available evidence for health care interventions. 

## Getting studies


## Binary outcome variable

## Continuous outcome variable

## Fixed vs Random Effects Models

## Summary measure

## {meta}

## {metafor}
?metafor::dat.graves2010
Cholera information
meta::metabin

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

